### 2014-06-06 writing/S'14 paper/quantifiers.tex
Temp
Final results in!

\begin{table}[tp]
  \centering
  \begin{tabular}{ l rrr }
    \toprule
    Data & Most frequent class & 20 dim RNN (\%) & 20 dim RNTN (\%)\\
    \midrule
    \textsc{all split}	& 35.4 &	65.3&	\textbf{99.0}
    \\[1ex]    
    \textsc{pair two/less-than-two}	& 59.8 &	77.6 &	\textbf{100.0} \\
    \textsc{pair not-all/not-most}	&0 & 60.8 &	\textbf{82.0} \\
    \textsc{pair all/some}	& 0& 52.5  &	\textbf{85.1} \\
    \textsc{pair no/no}	& 30.8 &	68.9 &	\textbf{99.9} \\
    \bottomrule
  \end{tabular}
  \caption{Performance on the quantifier experiments. }
  \label{resultstable}
\end{table}

\paragraph{Results} 
The results for these experiments are shown in
Figure~\ref{resultstable}. We compare the results to a most frequent
class baseline, which reflects the frequency in the test data of most
frequent class in the training data, $\natind$.  After some
cross-validation, we chose 20-dimensional word and phrase
representations, and 75 dimensional feature vectors for the
classifier.

The RNN performed poorly at this task, even though the sentences used
in these examples are short enough to avoid the pathology shown in
Figure~\ref{prop-falloff}.  However, the perfect performance by the
RNTN on the \textsc{pair no/no} experiment and its strong performance
on \textsc{all split} and \textsc{pair two/less-than-two} suggests
that that this stronger model is able to handle quantifiers correctly
given sufficient training data, but the sub-90\% results on two of the
training settings suggest that it may not be able to generalize from
data this impoverished in general. However, though the question of how
much data is necessary to accurately capture quantifier behavior in a
na\"ive model remains open, the fact that both models perform far
above baseline is promising.

>>>>

\begin{table}[tp]
  \centering
  \begin{tabular}{ l rrr }
    \toprule
    Data & Most frequent class & 16 dim RNN  & 20 dim RNTN\\
    \midrule
    \textsc{all split}	& 35.4 (7.5) &	67.4 (56.5)&	\textbf{100.0 (100.0)}
    \\[1ex]    
    \textsc{pair two/less-than-two}	& 59.8 (18.4) &	77.2 (57.4) &	\textbf{100.0 (100.0)} \\
    \textsc{pair not-all/not-most}	&0 (0) & 66.0 (54.3) &	\textbf{93.8 (91.5)} \\
    \textsc{pair all/some}	& 0 (0) & 62.7 (65.9)  &	\textbf{78.4 (84.7)} \\
    \textsc{pair no/no}	& 30.8 (10.2) &	67.8 (61.8) &	\textbf{99.9 (99.7)} \\
    \bottomrule
  \end{tabular}
  \caption{Performance on the quantifier experiments. Results are reported as accuracy scores followed by macroaveraged F1 scores in parentheses.}
  \label{resultstable}
\end{table}

\paragraph{Results} 
The results for these experiments are shown in
Figure~\ref{resultstable}. We compare the results to a most frequent
class baseline, which reflects the frequency in the test data of most
frequent class in the training data, $\natind$.  After some
cross-validation, we chose 16 and 20-dimensional
representations for the RNN and RNTN respectively, and 75 dimensional 
feature vectors for the classifier.

The RNN performed poorly at this task, even though the sentences used
in these examples are short enough to avoid the pathology shown in
Figure~\ref{prop-falloff}.  However, the perfect performance by the
RNTN on the \textsc{all split} and \textsc{pair two/less-than-two} 
experiment and its strong performance on \textsc{pair no/no} suggests
that that this stronger model is able to handle quantifiers correctly
given sufficient training data, but the weaker results on two of the
training settings suggest that it may not be able to generalize from
data this impoverished in general. However, though the question of how
much data is necessary to accurately capture quantifier behavior in a
na\"ive model remains open, the fact that both models perform far
above baseline is promising.
